Augmenting the DonorsChoose.org Corpus for Meta-Learning

### 2019-02-15 doc/paper/main.tex
paper/main.tex: Add citations and amendments
Adapt literature.bib accordingly.

\section{Introduction}
Meta-Learning is the process of applying machine learning algorithms on metadata as is generated by a subsystem composed of machine learners. The goal of meta-learning systems is to improve existing approaches by combining the strengths of several single machine learning systems in an ensemble. In recommender systems it is an emerging field of interest as meta-learning promises to better sort through item, user and transaction information as to retrieve the best possible match of item and user.

@@

Our objective is to address the data augmentation part in a comprehensive way as to allow researchers to focus on the actual meta-learning evaluation. We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich, vast corpus is a suitable candidate. The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}). In place of a metric, the recall in Top-N set is chosen as it can be computed for a wide range of algorithms. It is further amended with aggregated statistics about users and items and metadata of an exemplary experiment.

>>>>

\section{Introduction}
Meta-Learning is the process of applying machine learning algorithms on metadata as generated by a subsystem composed of machine learners. The goal of meta-learning systems is to improve existing approaches by combining the strengths of several single machine learning systems~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}. In recommender systems it is an emerging field of interest as meta-learning promises to better sort through item-, user- and transaction-information as to retrieve the best possible match of item and user. In order to investigate meta-learning algorithms, the required metadata needs to be computed in advance.

@@

Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning evaluation. We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich, vast corpus is a suitable candidate. The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}). In place of a metric, the recall in a Top-N set is used as it can be computed for a wide range of algorithms. The dataset is further amended with aggregated statistics about users and items and metadata of an exemplary experiment.
